### 2021-09-10 sections/healthcare_application/main.tex
Apply minor changes

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
    \item \( T_i \): The action that ED \(i\in\{1, 2\\) chooses to play which corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\\)
    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\\)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
    lost individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
the system unable to cope regardless of the decisions made.

>>>>

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
    \item \( T_i \): The action that ED \(i\in\{1, 2\} \) chooses to play which 
    corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\} \)
    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\} \)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
    lost individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes the loss in efficiency
due to rational individual behaviour decreases. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
the system unable to cope regardless of the decisions made.
